%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[10pt]{article} % Font size - 10pt, 11pt or 12pt

\usepackage[hmargin=1.25cm, vmargin=1.5cm]{geometry} % Document margins

\usepackage{ifsym} % Required for symbols in the colored box

\usepackage[usenames,dvipsnames]{xcolor} % Allows the definition of hex colors

% Fonts and tweaks for XeLaTeX
\usepackage{fontspec,xltxtra,xunicode}
\defaultfontfeatures{Mapping=tex-text}
%\setromanfont[Mapping=tex-text]{Hoefler Text} % Main document font
%\setsansfont[Scale=MatchLowercase,Mapping=tex-text]{Gill Sans} % Font for your name at the top
%\setmonofont[Scale=MatchLowercase]{Andale Mono}

% Colors for links, text and headings
\usepackage{hyperref}
\definecolor{linkcolor}{HTML}{2b2b2b} % Off-black color for links
\definecolor{shade}{HTML}{e5e4e2} % Platinum color for the contact information box
\definecolor{text1}{HTML}{2b2b2b} % Main document font color, off-black
\definecolor{headings}{HTML}{6A6A6A} % Light gray color for headings
% Other color palettes: shade=B9D7D9 and linkcolor=A40000; shade=D4D7FE and linkcolor=FF0080

\hypersetup{colorlinks,breaklinks, urlcolor=linkcolor, linkcolor=linkcolor} % Set up links and colors

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
% Headers and footers can be added with the \lhead{} \rhead{} \lfoot{} \rfoot{} commands
% Example footer:
%\rfoot{\color{headings} {\sffamily Last update: \today}. Typeset with Xe\LaTeX}

\renewcommand{\headrulewidth}{0pt} % Get rid of the default rule in the header

\usepackage{titlesec} % Allows creating custom \section's

% Format of the section titles
\titleformat{\section}{\color{headings}{\textbf}
\scshape\Large\raggedright}{}{0em}{}[\color{black}\titlerule]

\titlespacing{\section}{0pt}{0pt}{5pt} % Spacing around titles

\begin{document}

\color{text1} % Sets the default text color for the whole document to the color defined as 'text1'

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

\par{\centering{\sffamily\Large Adithya \textbf{Venkatesh}}\\ % Your name
%{\color{headings}\sffamily\Huge\fontspec{Freebooter Script}Curriculum {Vit\fontspec{Freebooter Script}\ae}\\[15pt]\par}
%{\color{headings}\fontspec[Variant = 2]{Zapfino} Curriculum {Vit\fontspec[Variant = 3]{Zapfino}\ae}\\[15pt]\par} % Curriculum vitae text in the Zapfino font
	
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\section{\uppercase{\textbf{Experience}}}

%------------------------------------------------
% AMAZON
%------------------------------------------------

{\raggedright\large Amazon Web Services \normalsize\textsc{ | Seattle, WA & Sydney, NSW} | 07/01/2019 - Current\\
\textbf{Senior SDE | Builders Tools}\\[5pt]}
\begin{itemize}\itemsep-0.25em
    \item I conceived an idea to massively tighten Amazon's dev-test cycle, allowing Amazon's builders to completely test changes before merging into mainline. This involved driving consensus across a 500-person organization; convincing directors, principal engineers, and a VP that this was the best use of our time.
    \item Bootstrapped a new organization in Australia, growing from 5-20+ engineers who consistently deliver delightful integration and load testing tools to Amazon engineers.
    \item Led a team of 40+ engineers spread across two timezones with the charter of helping Amazon builders ensure they were always producing high-quality software.
    \item Identified architectural redundancies in two Continuous Integration (CI) systems which drive ~99\% of Amazon's Continuous Integration (CI) traffic. I authored and delivered a 2-year plan to combine these systems, and consulted with 2x '2-pizza' teams to successfully merge them.
    \item Worked with senior engineers on the team to prototype a tool to dynamically understand traffic patterns and help Amazon's service owners comprehend the difference between customer behavior and test coverage.
    \item Member of the organization's 5-person incident response escalation team - I orchestrate resolution of high impact security and operational issues in my organization when frontline engineers need help
\end{itemize}\\


{\raggedright\large Amazon Web Services \normalsize\textsc{ | Seattle, WA} | 07/13/15 - 06/31/19\\
\textbf{SDE | Developer Tools}\\[5pt]}
\begin{itemize}\itemsep-0.25em
    \item Designed from scratch and lead a team of 7 engineers to build tools for continuous/canary testing to help service owners identify issues and pre-empt negative customer impact.
    \item Owned and launched a fully-managed cross-vertical (integration, load, canary) test orchestration platform used by 50\% of Amazon's teams.
    \item Constantly finding ways to evangelize Builder Tools products and educate new engineers; led workshops, bootcamps and talks.
    \item AWS CodeBuild pre launch team - One of three engineers selected from my VP's org to spur the launch effort of AWS CodeBuild in time for re:Invent!
    \item Promoted to SDE-2 on 2017-04-01
\end{itemize}\\

%------------------------------------------------
% PROJECTS
%------------------------------------------------
{\raggedright\large Academic Projects \normalsize\textsc{ | 2013 - 2015\\}
\begin{itemize}\itemsep-0.25em
    \item \textbf{Graduate | Cornell University} - Developed a fast, scalable cryptocurrency exchange built on top of Bitcoin, Dogecoin, Flask, and Hyperdex | Protoype built to display NoSQL performance with ACID transactions capabilities of Hyperdex (built in Emin Gun Sirer's lab)
    \item \textbf{Undergraduate | Inmobi} - Prototyped two projects 1) An Integration Test framework for a chef-based deployment platform with JenkinsCI, test-kitchen and minitest-handler 2) A platform that enabled analysis of source quality and build metrics at Inmobi
    \item \textbf{Summer Research | Concordia University} - Researched and implemented a ‘CDMA Protocol in Multi-channel Multi-Radio Wireless Mesh Networks’ with Prof Brigitte Jaumard.
    \item \textbf{Summer Research | IIT Bombay} - Research algorithmic solutions and improvements to simulate CNC Machining using Octree and Quadtree data structures.
\end{itemize}\\

%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.49\textwidth} % Start the left-hand side of the page

%----------------------------------------------------------------------------------------
%	COLORED BOX
%----------------------------------------------------------------------------------------

\vspace{10pt}
\colorbox{shade}{
    \textcolor{text1}{
        \begin{tabular}{r|p{4cm}}
            \raisebox{-1pt}{\Letter} & \href{mailto:adithyavenk@gmail.com}{adithyavenk@gmail.com} \\ % Email address
            \raisebox{-3pt}{\Mobilefone} & +1 972-567-0504 \\ % Phone number
            LinkedIn & \href{https://www.linkedin.com/in/adithyavenkatesh}{\custombold{in/adithyavenkatesh}} \\
%            Github & \href{https://github.com/bloomark}{\custombold{bloomark}} \\
            Work Authorization & US H1B, Indian Citizen, AU Permanent Resident
        \end{tabular}
    }
}\\[10pt]

\end{minipage}
\begin{minipage}[t]{0.49\textwidth} % Start the right-hand side of the page

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{\textbf{Education}}

\begin{tabular}{rl} % Start a table with two columns, one for dates and one for qualifications

%------------------------------------------------
% EDUCATION 1
%------------------------------------------------

05/24/15 & \large{Cornell University,} \normalsize{USA}\\
& \textbf{MEng}, \textsc{Computer Science} \\ 
& \small Cum. GPA : 3.78 out of 4.0\\
&\\
	 
%------------------------------------------------
% EDUCATION 2
%------------------------------------------------

06/06/14 & \large{M. S. Ramaiah Institute of} \\
& \large{Technology,} \normalsize{INDIA} \\
&  \textbf{B.E.} \textsc{Computer Science} \\ 
& \small Cum. GPA : 9.02 out of 10.0\\
&\\
\end{tabular}\\[10pt]

\end{minipage} % End right-hand side of the page

\end{document}
